\section*{NeurIPS Paper Checklist}

\begin{enumerate}
\item \textbf{Claims}

Question: Do the main claims made in the abstract and introduction accurately
reflect the paper's contributions and scope?

Answer: \answerYes{}.

Justification: The abstract and introduction state that the work is a
small-sample calibration study and explicitly avoid claiming scored private-set
performance.

\item \textbf{Limitations}

Question: Does the paper discuss the limitations of the work?

Answer: \answerYes{}.

Justification: Section 8 discusses sample size, unscored private predictions,
missing confidence intervals, incomplete CoT/Hybrid reruns, and incomplete
structured-feature baselines.

\item \textbf{Theory assumptions and proofs}

Question: For each theoretical result, does the paper provide the full set of
assumptions and a complete proof?

Answer: \answerNA{}.

Justification: The paper is empirical and does not present new theoretical
results or proofs.

\item \textbf{Experimental reproducibility}

Question: Does the paper fully disclose the information needed to reproduce the
main experimental results?

Answer: \answerYes{}.

Justification: The paper reports datasets, scripts, model identifiers, sample
size, seed, prompts, Ollama endpoint, and no-thinking controls. The repository
contains the corresponding code and result CSVs.

\item \textbf{Open access to data and code}

Question: Does the paper provide open access to the data and code, with
sufficient instructions to reproduce the results?

Answer: \answerYes{}.

Justification: The public data and scripts are in the repository. The
private/blind file is used only for prediction generation and is not presented as
a scored benchmark.

\item \textbf{Experimental setting details}

Question: Does the paper specify all training and evaluation details needed to
understand the results?

Answer: \answerYes{}.

Justification: Sections 3--6 describe the split, sample size, model identifiers,
prompt strategies, decoding setup, output parser, and metrics.

\item \textbf{Statistical significance}

Question: Does the paper report uncertainty estimates or statistical
significance where appropriate?

Answer: \answerNo{}.

Justification: The paper explicitly identifies missing confidence intervals and
multi-seed evaluation as a limitation and next required step.

\item \textbf{Datasets}

Question: Does the paper describe the dataset characteristics and any relevant
privacy or licensing constraints?

Answer: \answerYes{}.

Justification: Section 3 describes the public and private/blind VCBench files,
the 9\% class imbalance, the missing private labels, and the anonymized founder
profile setting.

\item \textbf{Compute resources}

Question: Does the paper report the compute resources used?

Answer: \answerNo{}.

Justification: The current draft reports local Ollama inference and qualitative
runtime observations, but it does not yet include hardware specifications. This
should be added before submission.

\item \textbf{Broader impacts}

Question: Does the paper discuss both potential positive and negative societal
impacts?

Answer: \answerYes{}.

Justification: Section 9 discusses deployment risks, fairness concerns, prestige
proxies, and the need for human oversight in VC screening.

\item \textbf{Safeguards}

Question: Does the paper describe safeguards for responsible use where relevant?

Answer: \answerYes{}.

Justification: The paper frames the system as benchmark research, not a
deployment-ready screening system, and recommends fairness audits, calibration
monitoring, and human oversight.

\item \textbf{Licenses for existing assets}

Question: Are licenses for existing assets such as code, data, and models
identified where possible?

Answer: \answerNo{}.

Justification: The draft names the model and benchmark files, but model and
dataset license information should be verified and added before submission.
\end{enumerate}
